Figures

### 2019-10-02 figures/07_model-selection.Rmd
rebuild figures

```{r tp_fe, out.width="3.45in", out.height="4in"}
# lapply(re_brms, function(x) x $formula) 
# re_brms[[6]]$formula
best_tp        <- 6 # 6 is best tp model with random effects
fit_tp         <- re_brms[[best_tp]] 
signif_hu4_ids <- fit_tp$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)

>>>>

```{r tp_fe, out.width="3.45in", out.height="4in"}
# lapply(re_brms, function(x) x$R2)
# lapply(re_brms, function(x) x $formula) 
# re_brms[[6]]$formula
best_tp        <- 6 # 6 is best tp model with random effects
fit_tp         <- re_brms[[best_tp]] 
signif_hu4_ids <- fit_tp$re_signif_ids 
signif_hu4     <- dplyr::filter(hu4, ZoneID %in% signif_hu4_ids)
